financial Well Being Analysis

### 2024-11-26 paper/paper.qmd
Updated tests and simulations

@@

```{r}
#| echo: false
#| warning: false
#| message: false
library(skimr)
skim_summary <- data %>%
  select(-PUF_ID) %>%  # Remove 'PUF_ID' column
  select(where(is.numeric)) %>%  # Keep only numeric columns
  skim()

@@

# Linear Regression Model

@@

>>>>

## Significance

## Estimand

@@

## Overview

## Measurement

```{r}
#| echo: false
#| warning: false
#| message: false
library(skimr)
skim_summary <- data %>%
  #select(-PUF_ID) %>%  # Remove 'PUF_ID' column
  select(where(is.numeric)) %>%  # Keep only numeric columns
  skim()

@@

@@

- `validate` [@validate]: This package provide useful functions for data tests.
